Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-23 manuscript/climate_sensitivity_SI.Rmd
Rewrote SI list at end of main text

\newpage
```{r table S5, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
singlevar_table <- read.csv("tables_figures/publication/tableS5_singlevariable_models_lmer_arimaratio_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(singlevar_table, booktabs = TRUE, caption = "Table S5. Individual tests of species traits as drivers of drought resistance, where $Rt_{ARIMA}$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  kable_styling()
```
Variable abbreviations are as in Table 2. 
$\Delta$AICc is the AICc of a model excluding the trait minus that of the model including it.

@@

\newpage
```{r table S6, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS6_multivariable_models_lmer_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S6. Summary of top full models for each drought instance, where $Rt$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 6, 10, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 11, 16, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(6, bold = T) %>%
  row_spec(11, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold). 
$R^2$ refers to conditional $R^2$. 
Year was included in the model for all drought years, but its effect was not included in any top models, and coefficients were small (1966: 0, 1977: -0.019, 1999: -0.005; same values in all top models).

\newpage
```{r table S7, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS7_multivariable_models_lmer_arimaratio_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S7. Summary of top  models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 7, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 8, 14, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 15, 25, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(8, bold = T) %>%
  row_spec(15, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold). 
$R^2$ refers to conditional $R^2$. 
Year was included in the model for all drought years, but its effect was not included in any top models, and coefficients were small (1966: 0, 1977: -0.03, 1999: 0.008; same values in all top models).

>>>>

\newpage
```{r table S5, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
singlevar_table <- read.csv("tables_figures/publication/tableS5_singlevariable_models_lmer_arimaratio_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(singlevar_table, booktabs = TRUE, caption = "Table S5. Individual tests of species traits as drivers of drought resistance, where $Rt_{ARIMA}$ is used as the response variable.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  kable_styling()
```
Variable abbreviations are as in Table 2. 
$\Delta$AICc is the AICc of a model excluding the trait minus that of the model including it.

@@

\newpage
```{r table S6, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS6_multivariable_models_lmer_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S6. Summary of top full models for each drought instance, where $Rt$ is used as the response variable.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 6, 10, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 11, 16, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(6, bold = T) %>%
  row_spec(11, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold). 
$R^2$ refers to conditional $R^2$. 
Year was included in the model for all drought years, but its effect was not included in any top models, and coefficients were small (1966: 0, 1977: -0.019, 1999: -0.005; same values in all top models).

\newpage
```{r table S7, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS7_multivariable_models_lmer_arimaratio_CPout.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S7. Summary of top  models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  pack_rows("", 1, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 7, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 8, 14, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 15, 25, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(5, bold = T) %>%
  row_spec(8, bold = T) %>%
  row_spec(15, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 2.0 ($\Delta$AICc<1) of the best model (bold). 
$R^2$ refers to conditional $R^2$. 
Year was included in the model for all drought years, but its effect was not included in any top models, and coefficients were small (1966: 0, 1977: -0.03, 1999: 0.008; same values in all top models).

### 2020-07-23 manuscript/climate_sensitivity_draft.Rmd
Rewrote SI list at end of main text

*redo this list!!*

Table S1: Species-specific bark thickness regression equations

Table S2: Species-specific height regression equations

Table S3: Palmer drought severity index (PDSI) by month for focal droughts

Figure S1: Map of ForestGEO plot showing TWI and location of cored trees

Figure S2: Time series of Palmer Drought Severity Index (PDSI) for the 2.5 years prior to
each focal drought

Figure S3: Height (from reconstructed DBH) by crown position across the three focal droughts and in the year of
measurement (2018)

>>>>

Table S1: Monthly Palmer Drought Severity Index (PDSI), and its rank among all years between 1950 and 2009 (driest=1), for focal droughts.

Table S2: Species-specific bark thickness regression equations.

Table S3: Species-specific height regression equations.

Table S4. Individual tests of species traits as drivers of drought resistance, where $Rt$ is used as the response variable.

Table S5. Individual tests of species traits as drivers of drought resistance, where $Rt_{ARIMA}$ is used as the response variable.

Table S6. Summary of top full models for each drought instance, where $Rt$ is used as the response variable.

Table S7. Summary of top  models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable.

Figure S1. Time series of Palmer Drought Severity Index (PDSI) for the 2.5 years prior to each focal drought

Figure S2: Map of ForestGEO plot showing topographic wetness index and location of cored trees

Figure S3: Distribution of reconstructed tree heights across drought years.

Figure S4. Distribution of independent variables by species.

Figure S5. Comparison of $Rt$ and $Rt_{ARIMA}$ results, with residuals, for each drought scenario

Figure S6. Visualization of best model, with data, for all droughts combined.
